A Constraint Solving Approach to Parikh Images of Regular Languages

### 2024-03-08 evaluation.tex
small fixes

We obtain the results by executing \Ostrich{}~1.3 with CA-Str using
the same benchmarking infrastructure (the StarExec cluster)
and configuration that ran SMT-COMP~2023, combining our new results for CA-Str with the
published results of SMT-COMP~2023.
\footnote{StarExec Job ID 59410, \enquote{SMT-COMP 2023 single query final}, 
available at \url{https://www.starexec.org/starexec/secure/details/job.jsp?id=59410}.} 
Where avaiable, we use the revised, out-of
competition version of the results for solvers with bugs discovered during
the competition, including \Ostrich{} and Z3-Noodler. 
\footnote{StarExec Job ID 59668, \enquote{SMT-COMP 2023 single query final fixed} available at
\url{https://www.starexec.org/starexec/secure/details/job.jsp?id=59668}.}
Note that Z3-Noodler abstained on \numprint{70}~instances, and thus has a lower total number of results.
We used the parallel results for all solvers.

@@

These results are expected. It is known that automata-based string solvers (\Ostrich{}, Z3-Noodler) 
tend to perform better on unsatisfiable than on satisfiable benchmarks, compared to solvers
that do not utilize automata and directly work on regular expressions (cvc5, z3alpha).
This is not unexpected, as the computation of automata representations of regular 
constraints can be expensive, and might be unnecessary for satisfiable formulas.
In addition, the algorithm in \Ostrich{} has stronger theoretical completeness
guarantees than cvc5 and Z3-Str, and ensuring completeness often has an adverse
effect on performance in practice~\cite{ostrich,Z3-str,cvc5}.

>>>>

We obtain the results by executing \Ostrich{}~1.3 with CA-Str using
the same benchmarking infrastructure (the StarExec cluster)
and configuration that ran SMT-COMP~2023, combining our new results for CA-Str with the
published results of SMT-COMP~2023.
\footnote{StarExec Job ID 59410, \enquote{SMT-COMP 2023 single query final}, 
available at \url{https://www.starexec.org/starexec/secure/details/job.jsp?id=59410}.} 
Where available, we use the revised, out-of
competition version of the results for solvers with bugs discovered during
the competition, including \Ostrich{} and Z3-Noodler. 
\footnote{StarExec Job ID 59668, \enquote{SMT-COMP 2023 single query final fixed} available at
\url{https://www.starexec.org/starexec/secure/details/job.jsp?id=59668}.}
Note that Z3-Noodler abstained on \numprint{70}~instances, and thus has a lower total number of results.
We used the parallel results for all solvers.

@@

These results are not unexpected. It is known that automata-based string solvers (\Ostrich{}, Z3-Noodler) 
tend to perform better on unsatisfiable than on satisfiable benchmarks, compared to solvers
that do not utilize automata and directly work on regular expressions (cvc5, z3alpha).
The computation of automata representations of regular 
constraints can be expensive, and might be unnecessary for satisfiable formulas.
In addition, the algorithm in \Ostrich{} has stronger theoretical completeness
guarantees than cvc5 and Z3-Str, and ensuring completeness often has an adverse
effect on performance in practice~\cite{ostrich,Z3-str,cvc5}.

### 2024-03-08 main.tex
Add data statement
move acks
DOI
further project
Add metadata from the ACM Author Submission
small fixes

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{OOPSLA} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2023}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2018}           %% If different from \acmYear

@@

@@

%% Appendix
\appendix
\section{Appendix}
\input{appendix.tex}

>>>>

%%% The following is specific to OOPSLA1 '24 and the paper
%%% 'A Constraint Solving Approach to Parikh Images of Regular Languages'
%%% by Amanda Stjerna and Philipp Rümmer.
%%%
\setcopyright{rightsretained}
\acmDOI{10.1145/3649855}
\acmYear{2024}
\copyrightyear{2024}
\acmSubmissionID{oopslaa24main-p181-p}
\acmJournal{PACMPL}
\acmVolume{8}
\acmNumber{OOPSLA1}
\acmArticle{138}
\acmMonth{4}
\received{21-OCT-2023}
\received[accepted]{2024-02-24}

@@

\begin{acks}
  We thank the reviewers for insightful comments.
  This work was supported by
    the Swedish Research Council (VR)
    under grants~2018-04727 and 2021-06327, the Swedish Foundation for Strategic
    Research (SSF) under the project WebSec (Ref.\ RIT17-0011), and the
    Wallenberg project UPDATE.
\end{acks}

@@

%% Appendix
%\appendix
%\section{Appendix}
%\input{appendix.tex}
